---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dev = "svg"
)
```
# ggpmthemes

<!-- badges: start -->
[![R build status](https://github.com/PMassicotte/ggpmthemes/workflows/R-CMD-check/badge.svg)](https://github.com/PMassicotte/ggpmthemes/actions)
<!-- badges: end -->

Simple R package with custom ggplot2 themes.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("PMassicotte/ggpmthemes")
```
## Examples

### Theme Poppins
```{r example}
library(ggpmthemes)
library(ggplot2)

p <- ggplot(ToothGrowth, aes(x = dose, y = len, group = dose)) +
  geom_boxplot(aes(fill = factor(dose))) +
  facet_wrap(~supp)

p +
  theme_poppins()

p +
  theme_exo2()
```

Works also with `geom_text()`

```{r}
p <- ggplot(mtcars, aes(wt, mpg, label = rownames(mtcars))) +
  geom_text(check_overlap = TRUE)

p +
  theme_poppins()

p +
  theme_exo()
```

### Scientific format

```{r}
ggplot(mtcars, aes(wt, mpg, label = rownames(mtcars))) +
  geom_point() +
  scale_x_continuous(labels = scientific_10x)
```

Please note that the 'ggpmthemes' project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.
